Thermodynamic fragments for magic states in quantum computation

### 2021-03-22 notes/notes.tex
Tidied up stabilizer bound proof

>>>>

Whether we are dealing with $\rm{(C1)}$ or $\rm{(C2)}$ depends on the physical parameters $\beta$ and $\epsilon$ as follows:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta \leq \beta_{\star}$. Then, $0 \leq \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
	\item $\beta > \beta_{\star}$. Then, $ \epsilon_{\star} = 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}
